Variable Density Tesseroids: Gravity fields calculation in spherical coordinates using variable densities in depth

### 2017-08-01 manuscript/manuscript.tex
Modifications in manuscript

In this way, the numerical approximation efficiently improves its accuracy and
gives the user more control over the computation by allowing to stop the division of the tesseroids when their dimensions are lower than a certain value (e.g. less than 10cm).

@@

We have performed similar tests, but now with variable density spherical shell. From the infinite density functions that can be proposed, we have chosen two characteristic ones: a linear and an exponential functions.
The first one represents the simpler variation, while the second one symbolise the fastest varying function.
The analytical solutions for these two types of functions were previously obtained and shown in equations \ref{eq:shell-pot-linear} and \ref{eq:shell-pot-exp}.

>>>>

In this way, the numerical approximation efficiently improves its accuracy and
gives the user more control over the computation: it allows to stop the division of the tesseroids when their dimensions are lower than a certain value (e.g. less than 10cm), which does not modifies significantly the desired gravitational field.

@@

We have performed similar tests, but now with variable density spherical shell. From the infinite density functions that can be proposed, we have chosen two characteristic ones: a linear and an exponential functions.
The first one constitutes the simplest variation, while the second one represents the fastest varying function.
The analytical solutions for these two types of functions were previously obtained and shown in equations \ref{eq:shell-pot-linear} and \ref{eq:shell-pot-exp}.
